A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
some modification to first page, for length

\maketitle
\begin{abstract}
  Many implementations of research techniques that automatically repair software
  bugs target programs written in C. Work that targets Java often begins from, or at
  least compares to, direct translations of such techniques to a Java context.
  However, Java and C are very different languages, and so Java should be
  studied to inform understanding of how to translate existing approaches to target it.
  We conduct a large-scale study of bug-fixing commits
  to Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make observations that can be
  leveraged to guide high quality automatic software repair to target Java specifically,
  including common and uncommon statement replacements as conducted by human
  developers and the applicability of previously-proposed patch construction
  operators in the Java context. 
\end{abstract}

@@

\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} study
a similar set of questions in 5 projects. In this paper we have studied a much
larger dataset~\cite{dyer2013} with 380,125 repositories; we have studied more
statement types, and we have studied replacements, omitted from Zhong and Su's
analysis. Similar to our study in Section~\ref{sec:stmtstudy}, researchers have
studied AST-level changes~\cite{Martinez:2015ez} or line
changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
Although granularity differs, our approach is novel with respect to scale of
analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
understand the ``Plastic Surgery Hypothesis'' underlying certain types of
program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
analyze changes to Java programs to inform an automated repair technique, and
show that doing so results in higher-quality repairs; we study their templates
heuristically on a different dataset. Their results motivate studies of human
repairs, as it may result in better patches.  Long and Rinard learn
probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
significantly less precise and does not inform a new technique.  Rather, it
serves as a starting point for research on the repair of Java bugs.

>>>>

\maketitle
\begin{abstract}
  Many implementations of research techniques that automatically repair software
  bugs target programs written in C. Work that targets Java often begins from or
  compares to, direct translations of such techniques to a Java context.  
  However, Java and C are very different languages, and Java should be
  studied to inform the translation of existing approaches to target it.
  We conduct a large-scale study of bug-fixing commits
  to Java projects, focusing on assumptions underlying common
  search-based repair approaches.  We make observations that can be
  leveraged to guide high quality automatic software repair to target Java specifically,
  including common and uncommon statement replacements as conducted by human
  developers and the applicability of previously-proposed patch construction
  operators in the Java context. 
\end{abstract}

@@

\vspace{1ex} \noindent\textbf{Related work.} Zhong and Su~\cite{zhong2015} ask
some of the same questions we do, on  5 projects. We study a much
larger dataset~\cite{dyer2013} with 380,125 repositories; and we look at more
statement types, as well as replacements. Similar to our study in
Section~\ref{sec:stmtstudy}, researchers have 
studied AST-level~\cite{Martinez:2015ez} and line-level
changes~\cite{Asaduzzaman:2013gu, Asaduzzaman:2013df} across bug fixing commits.
Although the granularity differs, our approach is also novel with respect to scale of
analysis. Barr et al.~\cite{Barr14fse} studied changes to Java programs to
understand the ``Plastic Surgery Hypothesis'' underlying certain types of
program repair, an orthogonal concern. Kim et al.~\cite{kim2013} manually
analyze changes to Java programs to inform automated repair, and
show that doing so results in higher-quality repairs; we study their templates
heuristically on a different dataset. Their results motivate studies of human
repairs, as it may result in better patches.  Long and Rinard learn
probabilistic models from bug fixes to C code~\cite{Long2016}. Our analysis is
significantly less precise and does not inform a new technique.  Rather, it
serves as a starting point for research on the repair of Java bugs.
